---
title: "GAM model comparisons"
author: "Trent Henderson"
date: "08/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
library(tidyverse)
library(readxl)
library(janitor)
library(data.table)
library(mgcv)
library(broom)
library(ggpubr)
library(Cairo)
library(visreg)

options(scipen = 999)

d <- read.csv("Everything.csv") %>%
  clean_names()
```

## About this document

This is a summary of initial Generalised Additive Model (GAM) statistical models which aim to explore predictors of reassurance activation in three regions of the brain:

1. Amygdala
2. Medial prefrontal cortex (MPFC)
3. Auditory cortex (AI)

The predictors used in the models included:

* Stress (DASS)
* Inadequate forms criticism
* Fear of expressing compassion to self

This document shows comparisons between different GAMs where the "Stress" variable from the DASS is either includedor excluded.

## Results

This section is organised according to the three brain region activation response variables.

### Amygdala reassurance

#### Complex model (with stress)

No predictors "significantly" predict amygdala reassurance.

```{r, echo = FALSE, message = FALSE}
amyg_re_gam_full <- gam(amygdala_reassurance ~ s(s_dass_stress) + s(t_fscrs_inad) + 
                     s(fears_of_expressing_compassion_to_self),
                   data = d)
summary(amyg_re_gam_full)
```

#### Parsimonious model (without stress)

No predictors "significantly" predict amygdala reassurance.

```{r, echo = FALSE, message = FALSE}
amyg_re_gam_pars <- gam(amygdala_reassurance ~ s(t_fscrs_inad) + 
                     s(fears_of_expressing_compassion_to_self),
                   data = d)
summary(amyg_re_gam_pars)
```

### MPFC

#### Complex model (with stress)

Inadequate forms is a significant predictor.

```{r, echo = FALSE, message = FALSE}
mpfc_re_gam_full <- gam(mpfc_reassuring ~ s(s_dass_stress) + s(t_fscrs_inad) + 
                     s(fears_of_expressing_compassion_to_self),
                   data = d)
summary(mpfc_re_gam_full)
```

#### Parsimonious model (without stress)

Inadequate forms is a significant predictor.

```{r, echo = FALSE, message = FALSE}
mpfc_re_gam_pars <- gam(mpfc_reassuring ~ s(t_fscrs_inad) + 
                          s(fears_of_expressing_compassion_to_self),
                        data = d)
summary(mpfc_re_gam_pars)
```

#### Model selection

Residuals are very close between the models.

```{r, echo = FALSE, message = FALSE}
sum(abs(residuals(mpfc_re_gam_full)))
sum(abs(residuals(mpfc_re_gam_pars)))
```

AIC values are virtually indistinguishable between the models.

```{r, echo = FALSE, message = FALSE}
AIC(mpfc_re_gam_full)
AIC(mpfc_re_gam_pars)
```

Deviance explained is also quite close between the models considering one omits a whole variable.

```{r, echo = FALSE, message = FALSE}
summary(mpfc_re_gam_full)$dev.expl
summary(mpfc_re_gam_pars)$dev.expl
```

#### Plots

The models are too close to justify the complex model (with stress). The below plots show the relationships for the parsimonious model (without stress).

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
p3 <- visreg(mpfc_re_gam_pars, "t_fscrs_inad", gg = TRUE, ylab = "MPFC reassurance")
p4 <- visreg(mpfc_re_gam_pars, "fears_of_expressing_compassion_to_self", gg = TRUE, 
       ylab = "MPFC reassurance")

ggarrange(p3,p4, nrow = 2)
```

### AI

#### Complex model (with stress)

Inadequate forms is a significant predictor.

```{r, echo = FALSE, message = FALSE}
ai_re_gam_full <- gam(ai_reassurance ~ s(s_dass_stress) + s(t_fscrs_inad) + 
                   s(fears_of_expressing_compassion_to_self),
                 data = d)
summary(ai_re_gam_full)
```

#### Parsimonious model (without stress)

Inadequate forms is a significant predictor.

```{r, echo = FALSE, message = FALSE}
ai_re_gam_pars <- gam(ai_reassurance ~ s(t_fscrs_inad) + 
                   s(fears_of_expressing_compassion_to_self),
                 data = d)
summary(ai_re_gam_pars)
```

#### Model selection

Residuals are very close between the models.

```{r, echo = FALSE, message = FALSE}
sum(abs(residuals(ai_re_gam_full)))
sum(abs(residuals(ai_re_gam_pars)))
```

AIC values are virtually indistinguishable between the models.

```{r, echo = FALSE, message = FALSE}
AIC(ai_re_gam_full)
AIC(ai_re_gam_pars)
```

Deviance explained is also quite close between the models considering one omits a whole variable.

```{r, echo = FALSE, message = FALSE}
summary(ai_re_gam_full)$dev.expl
summary(ai_re_gam_pars)$dev.expl
```

#### Plots

The models are too close to justify the complex model (with stress). The below plots show the relationships for the parsimonious model (without stress).

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
p5 <- visreg(ai_re_gam_pars, "t_fscrs_inad", gg = TRUE, ylab = "AI reassurance")
p6 <- visreg(ai_re_gam_pars, "fears_of_expressing_compassion_to_self", gg = TRUE, 
       ylab = "AI reassurance")

ggarrange(p5,p6, nrow = 2)
```


## Next steps

I have also run GAM vs GLM comparisons, but the GAMs almost always won out - this is most likely due to the nonlinear relationships seen in some of the plots. I have also done all of these relationships in a Bayesian framework which yielded interesting probabilistic results.
