---
title: "Prelim Bayesian reassurance outputs"
author: "Trent Henderson"
date: "07/05/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
library(tidyverse)
library(readxl)
library(janitor)
library(data.table)
library(mgcv)
library(broom)
library(ggpubr)
library(Cairo)
library(rstanarm)
library(bayesplot)

options(scipen = 999)

d <- read.csv("Everything.csv") %>%
  clean_names()
```

## About this document

This is a summary of initial Bayesian statistical models which aim to explore predictors of reassurance activation in three regions of the brain:

1. Amygdala
2. Medial prefrontal cortex (MPFC)
3. Auditory cortex (AI)

The predictors used in the models included:

* Stress (DASS)
* Inadequate forms criticism
* Fear of expressing compassion to self

## Results

This section is organised according to the three brain region activation response variables.

### Amygdala reassurance

Posterior distributions of the predictors.

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
invisible(amyg_re_bayes <- stan_glm(amygdala_reassurance ~ s_dass_stress + t_fscrs_inad + 
                            fears_of_expressing_compassion_to_self,
                          data = d,
                          family = gaussian(),
                          seed = 123)) # Uses default weakly informative priors

# Plots

amyg_re_bayes_posterior <- as.array(amyg_re_bayes)

mcmc_areas(amyg_re_bayes_posterior,
           pars = c("s_dass_stress", "t_fscrs_inad", "fears_of_expressing_compassion_to_self"),
           prob = 0.8) +
  labs(title = "Amygdala reassurance posterior distributions",
       subtitle = "Includes medians and 80% intervals")
```

A sample of posterior draws highlight an interesting pattern.

```{r, echo = FALSE, message = FALSE}
ppc_dens_overlay(y = amyg_re_bayes$y,
                 yrep = posterior_predict(amyg_re_bayes, draws = 100)) +
  labs(title = "Amygdala reassurance posterior predictions",
       subtitle = "Draws = 100")
```

Trace plots suggest no issues with convergence.

```{r, echo = FALSE, message = FALSE}
mcmc_trace(amyg_re_bayes_posterior, pars = c("(Intercept)", "sigma"), 
           facet_args = list(ncol = 1, strip.position = "left"))
```

Bayesian uncertainty intervals.

```{r, echo = FALSE, message = FALSE}
posterior_interval(amyg_re_bayes, prob = 0.95,
                                       pars = c("s_dass_stress", "t_fscrs_inad", 
                                                "fears_of_expressing_compassion_to_self"))
```

### MPFC

Posterior distributions of the predictors.

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
invisible(mpfc_re_bayes <- stan_glm(mpfc_reassuring ~ s_dass_stress + t_fscrs_inad + 
                            fears_of_expressing_compassion_to_self,
                          data = d,
                          family = gaussian(),
                          seed = 123)) # Uses default weakly informative priors

# Plots

mpfc_re_bayes_posterior <- as.array(mpfc_re_bayes)

mcmc_areas(mpfc_re_bayes_posterior,
           pars = c("s_dass_stress", "t_fscrs_inad", "fears_of_expressing_compassion_to_self"),
           prob = 0.8) +
  labs(title = "MPFC reassurance posterior distributions",
       subtitle = "Includes medians and 80% intervals")
```

A sample of posterior draws highlight an interesting pattern.

```{r, echo = FALSE, message = FALSE}
ppc_dens_overlay(y = mpfc_re_bayes$y,
                 yrep = posterior_predict(mpfc_re_bayes, draws = 100)) +
  labs(title = "MPFC reassurance posterior predictions",
       subtitle = "Draws = 100")
```

Trace plots suggest no issues with convergence.

```{r, echo = FALSE, message = FALSE}
mcmc_trace(mpfc_re_bayes_posterior, pars = c("(Intercept)", "sigma"), 
           facet_args = list(ncol = 1, strip.position = "left"))
```

Bayesian uncertainty intervals suggest that there is essentially zero probability that inadequate forms of criticism is < 0.

```{r, echo = FALSE, message = FALSE}
posterior_interval(mpfc_re_bayes, prob = 0.95,
                                       pars = c("s_dass_stress", "t_fscrs_inad", 
                                                "fears_of_expressing_compassion_to_self"))
```

Model criticisms show that there aren't many outliers outside the 0.5 threshold which may impact the model.

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
invisible(mpfc_re_bayes_small <- update(mpfc_re_bayes, formula. = . ~ . + I(s_dass_stress^2)))

mpfc_re_bayes_loo_1 <- loo(mpfc_re_bayes) # Leave-one-out cross validation
mpfc_re_bayes_loo_2 <- loo(mpfc_re_bayes_small)

par(mfrow = 1:2, mar = c(5,3.8,1,0) + 0.1, las = 3)
plot(mpfc_re_bayes_loo_1, label_points = TRUE)
plot(mpfc_re_bayes_loo_2, label_points = TRUE)
```

### AI

Posterior distributions of the predictors.

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
invisible(ai_re_bayes <- stan_glm(ai_reassurance ~ s_dass_stress + t_fscrs_inad + 
                            fears_of_expressing_compassion_to_self,
                          data = d,
                          family = gaussian(),
                          seed = 123)) # Uses default weakly informative priors

# Plots

ai_re_bayes_posterior <- as.array(ai_re_bayes)

mcmc_areas(ai_re_bayes_posterior,
           pars = c("s_dass_stress", "t_fscrs_inad", "fears_of_expressing_compassion_to_self"),
           prob = 0.8) +
  labs(title = "AI reassurance posterior distributions",
       subtitle = "Includes medians and 80% intervals")
```

A sample of posterior draws highlight an interesting pattern.

```{r, echo = FALSE, message = FALSE}
ppc_dens_overlay(y = ai_re_bayes$y,
                 yrep = posterior_predict(ai_re_bayes, draws = 100)) +
  labs(title = "AI reassurance posterior predictions",
       subtitle = "Draws = 100")
```

Trace plots suggest no issues with convergence.

```{r, echo = FALSE, message = FALSE}
mcmc_trace(ai_re_bayes_posterior, pars = c("(Intercept)", "sigma"), 
           facet_args = list(ncol = 1, strip.position = "left"))
```

Bayesian uncertainty intervals suggest that there is essentially zero probability that inadequate forms of criticism is < 0.

```{r, echo = FALSE, message = FALSE}
posterior_interval(ai_re_bayes, prob = 0.95,
                   pars = c("s_dass_stress", "t_fscrs_inad", 
                            "fears_of_expressing_compassion_to_self"))
```

Model criticisms show that there aren't many outliers outside the 0.5 threshold which may impact the model.

```{r, echo = FALSE, message = FALSE, results = 'hide',fig.keep = 'all', warning = FALSE}
invisible(ai_re_bayes_small <- update(ai_re_bayes, formula. = . ~ . + I(s_dass_stress^2)))

ai_re_bayes_loo_1 <- loo(ai_re_bayes) # Leave-one-out cross validation
ai_re_bayes_loo_2 <- loo(ai_re_bayes_small)

par(mfrow = 1:2, mar = c(5,3.8,1,0) + 0.1, las = 3)
plot(ai_re_bayes_loo_1, label_points = TRUE)
plot(ai_re_bayes_loo_2, label_points = TRUE)
```

## Next steps

Frequentist analysis using Generalised Additive Models (GAM) have also be completed. It will be determined whether this or the Bayesian approach should be used.
